Title

### 2023-10-16 Article.tex
Correct labels positions in sections

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Artificial Neural Network flow law\label{sec:ANN}}
%----------------------------------------------------------------------------------
As already proposed in Pantalé \eal \cite{Pantale-2021-EIN, Pantale-2023-DIA}, the approach used here is to implement the constitutive flow law defined by a trained ANN as a Fortran 77 subroutine into the Abaqus finite element code. 
The ANN is trained on the basis of the Gleeble experiments as already introduced in section \ref{sec:Introduction} and is used to compute the value of the flow stress $\sigma$ as a function of the strain $\varepsilon$, the strain rate $\mdot{\varepsilon}$ and the temperature $T$.
After the training phase, the weights and biases of the ANN are transcoded into a Fortran 77 subroutine wich is compiled and linked with lthe libraries of the Abaqus FE code to include the thermomechanical behavior and compute the flow tress and its three derivatives $\partial\sigma/\partial\varepsilon$, $\partial\sigma/\partial\mdot{\varepsilon}$ and $\partial\sigma/\partial T$ needed by the radial-return algorithm of the FE code.

\subsection{ANN governing equations\label{subsec:ANN-eqn}}

\subsubsection{Network architecture\label{subsubsec:ANN-arch}}
According to Figure \ref{fig:ANN-2HL}, the Artificial Neural Network used for computing the flow stress $\sigma$ from the strain $\varepsilon$, the strain rate $\mdot{\varepsilon}$ and the temperature $T$ is a two hidden layers network as already proposed by Pantalé \eal \cite{Pantale-2021-EIN, Pantale-2023-DIA}.
\begin{figure}[h]
\centering
\includegraphics[width=0.55\columnwidth]{Figures/ANN-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons ($\varepsilon$, $\mdot{\varepsilon}$ and $T$) and 1 output neuron ($\sigma$).}
\label{fig:ANN-2HL}
\end{figure}
Conforming to the structure presented in Figure \ref{fig:ANN-2HL}, the input of the neural network is a three component vector noted $\overrightarrow{x}$.

@@

\subsubsection{Activation functions\label{subsubsec:ANN-act}}

@@

\subsubsection{Pre and post processing architecture\label{subsubsec:ANN-pre}}
As we are using activations functions enhancing vanishing gradients for large values, the three inputs as well as the output must be normalized within the range $[0,1]$ to avoid ill-conditioning of the neural network.
This range has been chosen because we will use the Sigmoid activation function as one of the six proposed formulations, while this later squashed the output to the lowest range $[0,1]$.

@@

\subsubsection{Derivatives of the Neural Network\label{subsubsec:ANN-der}}

@@

\subsection{Training of the ANN on experimental data\label{subsec:train}}

@@

%----------------------------------------------------------------------------------
\section{Numerical simulations using the ANN flow law\label{sec:Numerical}}
%----------------------------------------------------------------------------------

\subsection{Numerical implementation of the ANN flow law\label{subsec:Num-impl}}

\subsection{Numerical simulations and comparisons\label{subsec:Num-sim}}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/vonMises}
\caption{xx.}
\label{fig:Num-misesTH}
\end{figure}
%----------------------------------------------------------------------------------
\section{Conclusions and future work\label{sec:Conclusions}}
%----------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}\label{sec:Appendix}

>>>>

%----------------------------------------------------------------------------------
\section{Introduction}\label{sec:Introduction}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Artificial Neural Network flow law}\label{sec:ANN}
%----------------------------------------------------------------------------------
As already proposed in Pantalé \eal \cite{Pantale-2021-EIN, Pantale-2023-DIA}, the approach used here is to implement the constitutive flow law defined by a trained ANN as a Fortran 77 subroutine into the Abaqus finite element code. 
The ANN is trained on the basis of the Gleeble experiments as already introduced in section \ref{sec:Introduction} and is used to compute the value of the flow stress $\sigma$ as a function of the strain $\varepsilon$, the strain rate $\mdot{\varepsilon}$ and the temperature $T$.
After the training phase, the weights and biases of the ANN are transcoded into a Fortran 77 subroutine wich is compiled and linked with lthe libraries of the Abaqus FE code to include the thermomechanical behavior and compute the flow tress and its three derivatives $\partial\sigma/\partial\varepsilon$, $\partial\sigma/\partial\mdot{\varepsilon}$ and $\partial\sigma/\partial T$ needed by the radial-return algorithm of the FE code.

\subsection{ANN governing equations}\label{subsec:ANN-eqn}

\subsubsection{Network architecture}\label{subsubsec:ANN-arch}
According to Figure \ref{fig:ANN-2HL}, the Artificial Neural Network used for computing the flow stress $\sigma$ from the strain $\varepsilon$, the strain rate $\mdot{\varepsilon}$ and the temperature $T$ is a two hidden layers network as already proposed by Pantalé \eal \cite{Pantale-2021-EIN, Pantale-2023-DIA}.
\begin{figure}[h]
\centering
\includegraphics[width=0.55\columnwidth]{Figures/ANN-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons ($\varepsilon$, $\mdot{\varepsilon}$ and $T$) and 1 output neuron ($\sigma$).}
\label{fig:ANN-2HL}
\end{figure}
Conforming to the structure presented in Figure \ref{fig:ANN-2HL}, the input of the neural network is a three component vector noted $\overrightarrow{x}$.

@@

\subsubsection{Activation functions}\label{subsubsec:ANN-act}

@@

\subsubsection{Pre and post processing architecture}\label{subsubsec:ANN-pre}
As we are using activations functions enhancing vanishing gradients for large values, the three inputs as well as the output must be normalized within the range $[0,1]$ to avoid ill-conditioning of the neural network.
This range has been chosen because we will use the Sigmoid activation function as one of the six proposed formulations, while this later squashed the output to the lowest range $[0,1]$.

@@

\subsubsection{Derivatives of the Neural Network}\label{subsubsec:ANN-der}

@@

\subsection{Training of the ANN on experimental data}\label{subsec:train}

@@

%----------------------------------------------------------------------------------
\section{Numerical simulations using the ANN flow law}\label{sec:Numerical}
%----------------------------------------------------------------------------------

\subsection{Numerical implementation of the ANN flow law}\label{subsec:Num-impl}

\subsection{Numerical simulations and comparisons}\label{subsec:Num-sim}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/vonMises}
\caption{xx.}
\label{fig:Num-misesTH}
\end{figure}
%----------------------------------------------------------------------------------
\section{Conclusions and future work}\label{sec:Conclusions}
%----------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
%\appendixstart
%\appendix
%\section[\appendixname~\thesection]{}\label{sec:Appendix}
